---
title: "Rethinking Practice"
author: "Cori Lopazanski"
date: "1/20/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Methods for Generating Posterior Distribution

## Grid Approximation

- Consider finite grid of parameter vlaues to approximate continuous distribuiton
- Often not practical IRL with multiple parameters, but useful learning tool

Steps:
1. Define grid: make list of parameter values
2. Compute prior at each parameter value on the grid
3. Compute likelihood at each parameter value
4. Compute unstandardized posterior (prior * likelihood)
5. Standardize posterior (each value/sum(all values))

```{r}
# define grid
p_grid <- seq(from = 0, to = 1, length.out = 5)

# define prior
prior <- rep(1, length(p_grid))

# compute likelihood at each value in grid
likelihood <- dbinom(6, size = 9, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior <- likelihood * prior

# standardize the posterior, so it sums to 1
posterior <- unstd.posterior / sum(unstd.posterior)

# plot the computed posterior distribution
plot(p_grid, posterior, type="b",
    xlab="probability of water", 
    ylab="posterior probability")
mtext("5 points")
```

More points increases the precision in the approximation: 

```{r}
# define grid
p_grid <- seq(from = 0, to = 1, length.out = 20)

# define prior
prior <- rep(1, 20)

# compute likelihood at each value in grid
likelihood <- dbinom(6, size = 9, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior <- likelihood * prior

# standardize the posterior, so it sums to 1
posterior <- unstd.posterior / sum(unstd.posterior)

# plot the computed posterior distribution
plot(p_grid, posterior, type="b",
    xlab="probability of water", 
    ylab="posterior probability")
mtext( "20 points" )
```


## Quadratic Approximation



